\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{helvet} % Modern sans-serif font
\usepackage{fancyhdr}
\usepackage{array}

% Set sans-serif as default font family
\renewcommand{\familydefault}{\sfdefault}

% Color definitions (Professional Slate and Navy theme)
\definecolor{primary}{HTML}{1A365D} % Deep Navy
\definecolor{text}{HTML}{2D3748}    % Charcoal Gray
\definecolor{lighttext}{HTML}{718096} % Cool Gray
\definecolor{linkcolor}{HTML}{2B6CB0} % Professional Blue for Links

% Configure hyperref
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
    pdftitle={Lovesh Nagar Resume},
    pdfauthor={Lovesh Nagar}
}

% Set text color
\color{text}

% Section formatting
\titleformat{\section}
  {\color{primary}\normalfont\Large\bfseries}
  {}{0em}
  {}
  [{\color{primary}\titrule[1pt]\vspace{0.2em}}]

% Spacing adjustments for section headers
\titlespacing*{\section}{0pt}{10pt}{6pt}

% Itemize settings for compact spacing
\setlist[itemize]{topsep=0pt,itemsep=2.5pt,parsep=0pt,leftmargin=1.5em}

% Page numbering configuration (fancyhdr)
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\rfoot{\color{lighttext}\small Page \thepage\ of 2}

% Custom command for job entries
\newcommand{\jobheader}[4]{
  \noindent\textbf{\large #1} \hfill \textbf{#2} \\
  \noindent\textsl{#3} \hfill \textsl{#4}
  \vspace{0.2em}
}

% Custom command for project entries
\newcommand{\projectheader}[3]{
  \noindent\textbf{\large #1} \hfill \textsl{#3} \\
  \noindent\href{#2}{\small\texttt{#2}}
  \vspace{0.2em}
}

\begin{document}

% ==================== HEADER ====================
\begin{center}
    {\Huge \bfseries \color{primary} LOVESH NAGAR} \\
    \vspace{0.4em}
    {\large Linux System Administrator \& Junior DevOps Engineer} \\
    \vspace{0.6em}
    \small
    Jaipur, Rajasthan --- 302015 \ \textbar\ \ 
    Phone: +91 6350458087 \ \textbar\ \ 
    Email: \href{mailto:nagarlavish99@gmail.com}{nagarlavish99@gmail.com} \\
    Portfolio: \href{https://loveshportfolio.netlify.app/}{loveshportfolio.netlify.app} \ \textbar\ \ 
    LinkedIn: \href{https://www.linkedin.com/in/lovesh-nagar}{linkedin.com/in/lovesh-nagar} \ \textbar\ \ 
    GitHub: \href{https://github.com/lovesh-nagar}{github.com/lovesh-nagar}
\end{center}

\vspace{-0.5em}

% ==================== SUMMARY ====================
\section*{PROFESSIONAL SUMMARY}
Linux System Administrator with 2+ years of experience deploying production applications and managing Apache/Nginx, Proxmox, and DNS/email infrastructure. Hands-on with Docker --- installation, troubleshooting, and container-based production deployments --- and with building/extending GitHub Actions CI/CD pipelines. Working knowledge of container orchestration fundamentals (Kubernetes/Minikube, Ingress), core AWS services, and Azure basics. Actively growing into Junior DevOps and Cloud Support roles on a strong Linux administration and automation foundation.

% ==================== TECHNICAL SKILLS ====================
\section*{TECHNICAL SKILLS}
\noindent
\begin{tabular}{@{}p{3.55in}p{3.55in}@{}}
    \textbf{Operating Systems:} RHEL, CentOS, Ubuntu & \textbf{CI/CD \& Version Control:} Git, GitHub, GitHub Actions, workflows \\
    \textbf{Web Servers:} Apache, Nginx, LiteSpeed & \textbf{Monitoring:} Prometheus, Grafana \\
    \textbf{Containers \& Orchestration:} Docker, Docker Compose, Kubernetes (Minikube), Ingress, Services, CNI basics & \textbf{Databases:} MySQL, MariaDB, PostgreSQL, MongoDB \\
    \textbf{AWS (Core Services):} EC2, S3, IAM, VPC, RDS, Route 53, ELB/ALB (Round Robin, Least Outstanding, routing), ECS, ECR, Lambda, CloudWatch & \textbf{Azure (Basics):} Virtual Machines (VMs), Entra ID (Active Directory) \\
    \textbf{Scripting \& Automation:} Bash, Cron Automation & \textbf{Virtualization:} Proxmox VE \\
    \textbf{Control Panels:} cPanel, Plesk, WHM & \textbf{Networking \& Protocols:} DNS, SSH, FTP, Crontab \\
\end{tabular}

% ==================== EXPERIENCE (PART 1) ====================
\section*{PROFESSIONAL EXPERIENCE}

\jobheader{CloudTechTiq Pvt. Ltd.}{Jaipur, India}{Linux System Administrator (Junior DevOps)}{Sept 2024 --- Present}
\begin{itemize}
    \item Deployed and maintained production-ready applications built in Node.js, Python (Uvicorn \& gunicorn), Laravel, and React across Apache/Nginx and PM2-managed environments.
    \item Installed and configured Docker on production Linux servers; containerized select Node.js and Python services for consistent, isolated deployments.
    \item Troubleshot container-level issues --- networking, volume mounts, and resource limits --- to minimize deployment downtime.
    \item Built and extended GitHub Actions CI/CD workflows, resolving pipeline and build failures to streamline deployment from commit to production.
    \item Diagnosed and resolved email deliverability issues using DNS records (SPF, DKIM, DMARC).
    \item Configured and managed virtual machines in Proxmox VE.
    \item Set up and maintained daily/weekly backup solutions for disaster recovery.
    \item Performed regular log monitoring, troubleshooting, and server patching to ensure system stability.
\end{itemize}

\clearpage

% ==================== EXPERIENCE (PART 2) ====================
\jobheader{GRRAS Solutions}{Jaipur, India}{Linux Intern}{May 2024 --- Sept 2024}
\begin{itemize}
    \item Installed and configured LAMP stack, deployed WordPress websites.
    \item Deployed Laravel and Magento applications; configured databases, cron jobs, and SSL.
    \item Gained practical experience with Docker volumes, partitions, and logical volumes (LVM).
    \item Set up DNS servers, handled log monitoring, SSH configuration, and cron automation.
    \item Practiced server security, service hardening, and network troubleshooting.
\end{itemize}

\vspace{0.8em}

\jobheader{Learn N Prep}{Kota, India}{Digital Marketing Executive (Freelance)}{Sept 2023 --- May 2024}
\begin{itemize}
    \item Managed Google Ads, Facebook Ads, and created SEO-rich content for YouTube and blogs.
    \item Performed basic server-side website updates; collaborated with the technical team on site deployments.
\end{itemize}

% ==================== KEY PROJECTS ====================
\section*{KEY PROJECTS}

\projectheader{DevBoard --- Three-Tier Containerized Application (React \textbar\ Go \textbar\ PostgreSQL)}{https://github.com/lovesh-nagar/Devboard-three-tier-application}{GitHub Repository}
\begin{itemize}
    \item Built and containerized a 3-tier app --- React/Vite frontend, Go REST API backend, PostgreSQL database --- with a dedicated Dockerfile per service.
    \item Orchestrated the stack with Docker Compose: health-check-based service dependencies, named volumes for data persistence, a custom bridge network, and .env-driven configuration.
    \item Designed a GitHub Actions CI/CD pipeline: automated lint \& test (ESLint, Go vet/test), Docker image build and push to Docker Hub, and CD deployment via a self-hosted runner (\texttt{docker compose pull \&\& up -d}).
    \item Added a Makefile to automate common operations (setup, up, down, logs, reset, smoke test).
\end{itemize}

\vspace{0.8em}

\projectheader{Flask App --- Dockerized AWS ECS Deployment}{https://github.com/lovesh-nagar/Docker-Deploy-Python}{GitHub Repository}
\begin{itemize}
    \item Containerized a Python Flask app using two build strategies --- single-stage and multi-stage distroless build --- reducing image size and attack surface for production.
    \item Built a \texttt{/health} endpoint for ALB/ECS target-group health checks.
    \item Mapped the AWS deployment path: pushed images to ECR, configured ECS task definitions \& services, and set up an Application Load Balancer target group for traffic routing.
    \item Automated Docker image build \& push to Docker Hub via GitHub Actions.
\end{itemize}

\vspace{0.8em}

% ==================== EDUCATION \& CERTIFICATIONS ====================
\noindent
\begin{tabular}{@{}p{3.55in}p{3.55in}@{}}
    \section*{EDUCATION} & \section*{CERTIFICATIONS} \\
    \textbf{B.A B.Ed} --- Pandit Deendayal Upadhyaya University \par \textsl{Timeline: 2021 --- 2025} & \textbullet\ \textbf{RHCSA} --- Red Hat Certified System Administrator \par \textsl{ID: 240-200-170} \\
    \textbf{DevOps Course} --- GRRAS Institute \par \textsl{Timeline: 2024} & \textbullet\ \textbf{EX188} --- Red Hat Specialist in Containers \par \textsl{ID: 240-200-170} \\
\end{tabular}

\vspace{0.8em}

% ==================== STRENGTHS \& OTHER ACHIEVEMENTS ====================
\noindent
\begin{tabular}{@{}p{3.55in}p{3.55in}@{}}
    \section*{OTHER ACHIEVEMENTS \& CLIENT SUPPORT} & \section*{CORE STRENGTHS} \\
    \textbullet\ Deployed 50+ React, Node, Python, Laravel apps on Linux & \textbullet\ Strong Linux fundamentals \& scripting \\
    \textbullet\ Real-time metrics dashboard using Prometheus/Grafana & \textbullet\ DevOps: Docker, Actions, K8s, Cloud (AWS/Azure) \\
    \textbullet\ Hardened servers (firewall, SSH keys, cron audits) & \textbullet\ Client ticketing communication \& L2 resolution \\
    \textbullet\ Managed client WHM/cPanel environments, SSL \& backups & \textbullet\ Adaptive learner of new tools \& frameworks \\
    \textbullet\ Automation of health checks via Bash and crontab & \textbullet\ High-pressure troubleshooting \\
    \textbullet\ Direct client interaction: deployments \& bug fixes & \textbullet\ Detail-oriented documentation skills \\
\end{tabular}

\end{document}
